\Title

### 2023-06-15 Grimaldi-etal-BiolCybernetics.tex
Perrinet2002

In a recent review, we reported experimental evidence for the presence of precise spiking motifs embedded in recordings from biological neural tissues~\cite{grimaldi_precise_2023}. In particular, \citet{abeles_role_1982} asked whether the role of cortical neurons is the integration of synaptic inputs or rather the detection of coincidences in temporal spiking motifs. While the first hypothesis favors the firing rate coding theory, the second emphasizes on the importance of temporal precision in neural activity. Since then, numerous studies have demonstrated the emergence of synchronous activity within a neuronal population~\citep{riehle_spike_1997, davis_spontaneous_2021}, efficient coding using precise spike timings~\citep{perrinet_coding_2004, gollisch_rapid_2008}, or precise timing in the auditory system~\citep{deweese_binary_2002, carr_circuit_1990}. All these findings and more~\citep{bohte_evidence_2004}, highlight the importance of the temporal aspect of the neural code and suggest the existence of spatiotemporal spiking motifs in biological spike trains. In neural models, the definition of heterogeneous delays~\citep{guise_bayesian_2014, zhang_supervised_2020, nadafian_bio-plausible_2020} allows the efficient detection of these spatiotemporal motifs embedded in the spike train. These spatiotemporal motifs present in neural activity may form useful representations to perform computations for various cognitive tasks using the synchrony of spikes reaching the soma of a neuron. In particular,~\citet{izhikevich_polychronization_2006} introduced the notion of the polychronous group as a spiking motif defined by a subset of neurons with different, but precise, relative spiking delays. This delay between a pair of connected neurons is defined as the time between the emission of a spike at the soma of the afferent neuron and its arrival at the soma of the efferent neuron. Importantly, due to the variety of weights and delays within a population, representations using polychronous groups have in theory a much higher information capacity than a firing rate-based approach.

>>>>

In a recent review, we reported experimental evidence for the presence of precise spiking motifs embedded in recordings from biological neural tissues~\cite{grimaldi_precise_2023}. In particular, \citet{abeles_role_1982} asked whether the role of cortical neurons is the integration of synaptic inputs or rather the detection of coincidences in temporal spiking motifs. While the first hypothesis favors the firing rate coding theory, the second emphasizes on the importance of temporal precision in neural activity. Since then, numerous studies have demonstrated the emergence of synchronous activity within a neuronal population~\citep{riehle_spike_1997, davis_spontaneous_2021}, efficient coding using precise spike timings~\citep{Perrinet2002,perrinet_coding_2004, gollisch_rapid_2008}, or precise timing in the auditory system~\citep{deweese_binary_2002, carr_circuit_1990}. All these findings and more~\citep{bohte_evidence_2004}, highlight the importance of the temporal aspect of the neural code and suggest the existence of spatiotemporal spiking motifs in biological spike trains. In neural models, the definition of heterogeneous delays~\citep{guise_bayesian_2014, zhang_supervised_2020, nadafian_bio-plausible_2020} allows the efficient detection of these spatiotemporal motifs embedded in the spike train. These spatiotemporal motifs present in neural activity may form useful representations to perform computations for various cognitive tasks using the synchrony of spikes reaching the soma of a neuron. In particular,~\citet{izhikevich_polychronization_2006} introduced the notion of the polychronous group as a spiking motif defined by a subset of neurons with different, but precise, relative spiking delays. This delay between a pair of connected neurons is defined as the time between the emission of a spike at the soma of the afferent neuron and its arrival at the soma of the efferent neuron. Importantly, due to the variety of weights and delays within a population, representations using polychronous groups have in theory a much higher information capacity than a firing rate-based approach.
